Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-04 Manuscript Analyses/manuscript_analysis.Rmd
formatting rmd file

rm(demo)

@@

rm(AM1_cor, PDM10_cor, cog_table, speaker_intel, demo_table)

@@

effect_plot(mods1, pic_seq_c, best_win)
effect_plot(mods1, best_win, pic_seq_c)
effect_plot(mods1, best_win, int = F)
effect_plot(mods1, list_sort_c, vocab_c)
effect_plot(mods1, vocab_c, list_sort_c)
effect_plot(mods1, list_sort_c, pattern_c)
effect_plot(mods1, pattern_c, list_sort_c)

@@

@@

effect_plot(mods2, vocab_c, pattern_c)
effect_plot(mods2, pattern_c, vocab_c)
effect_plot(mods2, best_win, int = F)
effect_plot(mods2, flanker_c, best_win)
effect_plot(mods2, best_win, flanker_c)
effect_plot(mods2, list_sort_c, pattern_c)
effect_plot(mods2, pattern_c, list_sort_c)
effect_plot(mods2, vocab_c, pic_seq_c)
effect_plot(mods2, pic_seq_c, vocab_c)
effect_plot(mods2, card_sort_c, vocab_c)
effect_plot(mods2, vocab_c, card_sort_c)

@@

effect_plot(mods12, list_sort_c, vocab_c)
effect_plot(mods12, vocab_c, list_sort_c)
effect_plot(mods12, list_sort_c, int = F)
effect_plot(mods12, pattern_c, int = F)
effect_plot(mods12, list_sort_c, flanker_c)
effect_plot(mods12, flanker_c, list_sort_c)

@@

effect_plot(mods22, vocab_c, pic_seq_c)
effect_plot(mods22, pic_seq_c, vocab_c)
effect_plot(mods22, vocab_c, int = F)
effect_plot(mods22, list_sort_c, flanker_c)
effect_plot(mods22, flanker_c, list_sort_c)

@@

initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)

mods_table %>%
  gt::gt() %>%
  cols_label(speaker = "Speaker",
             mods = "Model Specification",
             out_sample_r2 = "R\U00B2",
             out_sample_rmse = "RMSE")

change_mods <- rbind(AM1_change_mod, PDM10_change_mod)

change_mods %>%
  gt::gt() %>%
  cols_label(speaker = "Speaker",
             mods = "Model Specification",
             out_sample_r2 = "R\U00B2",
             out_sample_rmse = "RMSE")

>>>>

rm(demo, demo_table)

@@

rm(AM1_cor, PDM10_cor, cog_table, speaker_intel)

@@

effect_plot(mods1, pic_seq_c, best_win) # Picture Sequence Memory * Words in Noise
effect_plot(mods1, best_win, pic_seq_c) # Words in Noise * Picture Sequence Memory
effect_plot(mods1, best_win, int = F) # Words in Noise
effect_plot(mods1, list_sort_c, vocab_c) # Working Memory * Receptive Vocab
effect_plot(mods1, vocab_c, list_sort_c) # Receptive Vocab * Working Memory
effect_plot(mods1, list_sort_c, pattern_c) # Working Memory * Processing Speed
effect_plot(mods1, pattern_c, list_sort_c) # Processing Speed * Working Memory

@@

PDM10_initial_mod %>%
  gt::gt() %>%
  cols_label(speaker = "Speaker",
             mods = "Model Specification",
             out_sample_r2 = "R\U00B2",
             out_sample_rmse = "RMSE")

@@

effect_plot(mods2, vocab_c, pattern_c) # Receptive Vocab * Processing Speed
effect_plot(mods2, pattern_c, vocab_c) # Processing Speed * Receptive Vocab
effect_plot(mods2, best_win, int = F) # Words in Noise
effect_plot(mods2, flanker_c, best_win) # Inhibitory Control * Words in Noise
effect_plot(mods2, best_win, flanker_c) # Words in Noise * Inhibitory Control
effect_plot(mods2, list_sort_c, pattern_c) # Working Memory * Processing Speed
effect_plot(mods2, pattern_c, list_sort_c) # Processing Speech * Working Memory
effect_plot(mods2, vocab_c, pic_seq_c) # Receptive Vocab * Picture Sequence Memory
effect_plot(mods2, pic_seq_c, vocab_c) # Picture Sequence Memory * Receptive Vocab
effect_plot(mods2, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocab
effect_plot(mods2, vocab_c, card_sort_c) # Receptive Vocab * Cognitive Flexibility

# Mergining initial model summaries together
initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)

# Combining initial model figures and saving
p1 / p2
ggsave("Plots/Initial_mods.png", plot = last_plot(), width = 8, height = 10, units = "in")

# Removing unneeded items from Environment
rm(p1, p2, mods1, mods2, AM1_initial_mod, PDM10_initial_mod)

@@

effect_plot(mods12, list_sort_c, vocab_c) # Working Memory * Receptive Vocab
effect_plot(mods12, vocab_c, list_sort_c) # Receptive Vocab * Working Memory
effect_plot(mods12, list_sort_c, int = F) # Working Memory
effect_plot(mods12, pattern_c, int = F) # Processing Speed
effect_plot(mods12, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
effect_plot(mods12, flanker_c, list_sort_c) # Inhibitory Control * Working Memory

@@

effect_plot(mods22, vocab_c, pic_seq_c) # Receptive Vocab * Picture Sequence Memory
effect_plot(mods22, pic_seq_c, vocab_c) # Picture Sequence Memory * Receptive Vocab
effect_plot(mods22, vocab_c, int = F) # Receptive Vocab
effect_plot(mods22, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
effect_plot(mods22, flanker_c, list_sort_c) # Inhibitory Control * Working Memory

# Merging Model summaries together
change_mods <- rbind(AM1_change_mod, PDM10_change_mod)

# Combining and saving change model figures
p12 / p22
ggsave("Plots/Change_mods.png", plot = last_plot(), width = 8, height = 10, units = "in")

# Removing unneeded items from environment
rm(p12, p22, AM1_change_mod, PDM10_change_mod, mods12, mods22)

@@

# Creating Overall Model Table

initial_mods <- initial_mods %>%
  dplyr::mutate(outcome = "Initial Intelligibility")

change_mods <- change_mods %>%
  dplyr::mutate(outcome = "Intelligbility Change")

mods_table <- rbind(initial_mods, change_mods)

mods_table %>%
  gt::gt(groupname_col = "outcome") %>%
  cols_label(speaker = "Speaker",
             mods = "Model Specification",
             out_sample_r2 = "R\U00B2",
             out_sample_rmse = "RMSE") %>%
  gt::gtsave("Tables/mods_table.html")
